Assessing environmental and predator impacts on Antarctic Krill (*Euphausia superba*) population dynamics from an integrated length-to-age assessment model perspective

### 2025-06-14 MS2_Krill.Rmd
adding last chgs

```{r data-sources, eval=TRUE}
data <- data.frame(
  Source = c(
    "Krill Fishery Monitoring Program (CCAMLR SISO)",
    "Krill Fishery Monitoring Program (CCAMLR SISO)",
    "Krill Fishery Monitoring Program (CCAMLR SISO)",
    "AMLR Scientific Research Program",
    "Satellite Remote Sensing",
    "Predator Monitoring (MAPPPD)",
    "Predator Diet Composition (AMLR)"
  ),
  Description = c(
    "Total reported catches",
    "Standardized CPUE (by vessel, area, and depth)",
    "Length-frequency distributions (0.2 cm bins)",
    "Biomass indices by strata from net sampling",
    "Monthly chlorophyll-a concentration from EU Copernicus Marine Service (interpolated; doi:10.48670/moi-00021, doi:10.48670/moi-00148)",
    "Abundance by colony-specific trends of penguin populations",
    "Length-frequency of krill in predator diets"
  ),
  TimeSeries = c(
    "1997–2020",
    "1997–2020",
    "2000–2020",
    "1991–2011 (based on cruise periods)",
    "1997–present",
    "2000s–present",
    "1977–2020 (subset from 2000 used in this analysis)"
  ),
  SpatialScale = c(
    "By strata",
    "By strata",
    "By strata",
    "By strata",
    "Subarea 48.1",
    "By colony",
    "By colony"
  )
)

>>>>

```{r data-sources, eval=TRUE}
data <- data.frame(
  Source = c(
    "Krill Fishery Monitoring Program (CCAMLR SISO)",
    "Krill Fishery Monitoring Program (CCAMLR SISO)",
    "Krill Fishery Monitoring Program (CCAMLR SISO)",
    "AMLR Scientific Research Program",
    "Satellite Remote Sensing",
    "Predator Monitoring (MAPPPD)",
    "Predator Diet Composition (AMLR)"
  ),
  Description = c(
    "Total reported catches",
    "Standardized CPUE (by vessel, area, and depth)",
    "Length-frequency distributions (0.2 cm bins)",
    "Biomass indices by strata from net sampling",
    "Monthly chlorophyll-a concentration from EU Copernicus Marine Service (interpolated; doi:10.48670/moi-00021, doi:10.48670/moi-00148)",
    "Abundance by colony-specific trends of penguin populations",
    "Length-frequency of krill in predator diets"
  ),
  TemporalScale = c(
    "1997–2020",
    "1997–2020",
    "2000–2020",
    "1991–2011 (based on cruise periods)",
    "1997–present",
    "2000s–present",
    "1977–2020 (subset from 2000 used in this analysis)"
  ),
  SpatialScale = c(
    "By strata",
    "By strata",
    "By strata",
    "By strata",
    "Subarea 48.1",
    "By colony",
    "By colony"
  )
)
